Developing a preprint culture in biology

### 2013-03-05 ms.tex
legend for the table

Despite the success of this approach in other fields, most manuscripts in
biology are not posted to preprint servers and are therefore not seen by more
than a handful of other scientists prior to publication. In this article, we: 1)
highlight the advantages of open preprint servers for both scientists and
publishers; 2) discuss the preprint policies of major publishers in biology; and
3) review popular options to submit preprints.

@@

\begin{table}[!ht]
    \caption{\bf{Popular options for preprints}}
    \begin{tabular}{|l|cccccccc|}
    \hline
    Website               & Free & Comments & Private preprints & Moderated & Peer-reviewed & DOI & Version-Control & Other Content\\
    \hline
    arXiv.org             & Yes & No & No & Yes & No & No & No & No\\
    figshare.com          & Yes & Yes & No & No & No & Yes & No & Yes\\
    peerj.com             & 1/yr & Yes & Yes & No & No & Yes & No & No\\
    f1000research.com     & No & Yes & No & Yes & Yes & Yes & No & No\\
    github.com            & Yes & Yes & Yes & No & No & No & Yes & Yes\\
    \hline
    \end{tabular}
    \label{table:box1}
\end{table}

>>>>

Despite the success of this approach in other fields, most manuscripts in
biology are not posted to preprint servers and are therefore not seen by more
than a handful of other scientists prior to publication. In this article, we
highlight the advantages of open preprint servers for both scientists and
publishers and discuss the preprint policies of major publishers in biology.

@@

\begin{table}[!ht]
    \caption{\bf{Popular options for preprints}}
    \begin{tabular}{|l|cccccccc|}
    \hline
    Website               & Free & Comments & Private preprints & Peer-reviewed & DOI & Version-Control & Other Content\\
    \hline
    arXiv.org             & Yes & No & No & No & No & No & No\\
    figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
    peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
    f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
    github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
    \hline
    \end{tabular}
    \begin{flushleft}
    \textbf{Free:} Whether preprints can be submitted for free.
    \textbf{Comments:} Support for online comments on the item.
    \textbf{Private:} Support for private preprints.
    \textbf{Peer-reviewed:} Whether the preprints are peer-reviewed on the server.
    \textbf{DOI:} Each item is assigned a unique digital object identifier.
    \texbbf{Version-Control:} Is the preprint stored with a version-control system with the complete history of modifications?
    \textbf{Other content:} Can upload figures, videos, datasets, code.
    \end{flushleft}
    \label{table:box1}
\end{table}
